Through the eyes of the teacher

### 2022-03-08 01_studies/01_Laborstudie ProVisioNET/R script/demographic data/demographic data script.Rmd
SJT + demo data

# create a basic table (tibble) using tidyverse functions
demo.table <- demo.data %>%
  group_by(Group) %>%
  summarise(N=n(),
            "Gender male" = round(100 * n() / nrow(Gende)), 2,
            "M Age" = round(mean(Age), 2),
            "Min Age" = min(Age),
            "Max Age" = max(Age),
            "SD Age" = round(sd(Age), 2),
            "M Exp." = round(mean(`Teaching Experience`), 2),
            "Min Exp." = min(`Teaching Experience`),
            "Max Exp." = max(`Teaching Experience`),
            "SD Exp." = round(sd(`Teaching Experience`), 2),
           )

>>>>

# create a basic table (tibble) using tidyverse functions
demo.table <- demo.data %>%
  group_by(Group) %>%
  summarise(N=n(),
            "Male" = sum(Gender),
            "M Age" = round(mean(Age), 2),
            "Min Age" = min(Age),
            "Max Age" = max(Age),
            "SD Age" = round(sd(Age), 2),
            "M Exp." = round(mean(`Teaching Experience`), 2),
            "Min Exp." = min(`Teaching Experience`),
            "Max Exp." = max(`Teaching Experience`),
            "SD Exp." = round(sd(`Teaching Experience`), 2),
           )
